### 2022-05-23 manuscript.Rmd
Add discussion of familiarity preferences

# Re-run steps that take a long time?
run <- list(
  bayesian_models = TRUE,
  jackknife_analysis = TRUE,
  sensitivity_analysis = TRUE
)

@@

>>>>

# Re-run steps that take a long time?
run <- list(
  bayesian_models = FALSE,
  jackknife_analysis = FALSE,
  sensitivity_analysis = FALSE
)

@@

As a final statistical consideration, we have coded the effect size of the looking time difference between novel and familiar rotation events in a linear fashion. This means that a positive looking time difference (i.e., a novelty preference) is taken as stronger evidence for mental rotation than a looking time difference of zero (i.e., no systematic preference), which in turn is taken as stronger evidence for mental rotation than a negative looking time difference (i.e., a familiarity preference). Although novelty preference is the more paradigmatic case, some authors have argued that familiarity preference should also be taken as evidence for mental rotation ability [@erdmann2018; @moore2020; @johnson2020]. We have instead decided to model the looking time differences in a linear fashion to facilitate the interpretability of our models (for related discussion, see [@houston-price2004; @black2017; @cristia2018]). This procedure has rendered our meta-analytic effect sizes of mental rotation performance and of gender differences smaller than they would have been if both novelty preference and familiarity preference are interpreted as successful mental rotation.
